Capstone Movielens Report

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Draft report development: function `model.tune.param_range`, `tune_dir_path`, `cach_file_base_name`, `fn_tune.test.param_value` parameters described.

##### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function
\

@@

  - **loop_starter:** A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
For this purpose, the sequence step is calculated as follows:
$$
seq_step = \frac{end - start}{dvs}
$$

The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
```{r eval=FALSE}
seq(start, end, step)
```

  - **tune_dir_path:** ;
  - **cache_file_base_name:** ;
  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.;
  - **max.identical.min_RMSE.count:** ;
  - **is.cv:** ;
  - **endpoint.min_diff:** ;
  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.

>>>>

##### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
\

@@

###### Parameters
\
####### loop_starter 
\
A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
For this purpose, the sequence step is calculated as follows:
$$
step = \frac{end - start}{dvs}
$$

The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
```{r eval=FALSE}
seq(start, end, step)
```  
In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.

####### tune_dir_path 
\

To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the cache files are saved.

####### cache_file_base_name 
\

The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.

#######  fn_tune.test.param_value
\

This is a helper function name that is passed to the same-named parameter of the [tune.model_param] function that is called internally during the execution (see the [description of the `tune.model_param` function](#func.tune.model_param) above).

#######  
\

  - **max.identical.min_RMSE.count:** ;

#######  
\

  - **is.cv:** ;

#######  
\

  - **endpoint.min_diff:** ;

#######  
\

  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps

#######  
\

specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;

  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.

#######  
\

### 2025-05-11 reports/capstone-movielens-report.draft4.tex
Draft report development: function `model.tune.param_range`, `tune_dir_path`, `cach_file_base_name`, `fn_tune.test.param_value` parameters described.

\subparagraph{\texorpdfstring{\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
Function}{tune.model\_param Function}}\label{tune.model_param-function}

@@

\begin{itemize}
\tightlist
\item
  \textbf{loop\_starter:} A numeric vector of the form
  \texttt{c(start,\ end,\ dvs)}, where \texttt{start} and \texttt{end}
  are the endpoints of the interval on which the parameter value that
  minimizes \texttt{RMSE} is sought. \texttt{dvs} is a divisor for
  splitting the interval to transform it into a sequence of values among
  which the value that minimizes \texttt{RMSE} is sought. For this
  purpose, the sequence step is calculated as follows: \[
  seq_step = \frac{end - start}{dvs}
  \]
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \textbf{tune\_dir\_path:} ;
\item
  \textbf{cache\_file\_base\_name:} ;
\item
  \textbf{fn\_tune.test.param\_value:} A helper function that calculates
  the value of the \texttt{RMSE} for a given parameter value.;
\item
  \textbf{max.identical.min\_RMSE.count:} ;
\item
  \textbf{is.cv:} ;
\item
  \textbf{endpoint.min\_diff:} ;
\item
  \textbf{break.if\_min = TRUE:} A Boolean parameter that determines
  whether the function should terminate after completing the number of
  steps specified by the parameter \texttt{steps.beyond\_min}, after the
  minimum value of the \texttt{RMSE} has been found;
\item
  \textbf{steps.beyond\_min = 2:} (takes effect only if
  \texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the
  number of steps after finding the minimum value of the \texttt{RMSE},
  upon completion of which the function should terminate.
\end{itemize}

>>>>

\subparagraph{\texorpdfstring{\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
Function}{tune.model\_param Function}}\label{func.tune.model_param}

@@

\hfill\break
\#\#\#\#\#\#\# loop\_starter\\
A numeric vector of the form \texttt{c(start,\ end,\ dvs)}, where
\texttt{start} and \texttt{end} are the endpoints of the interval on
which the parameter value that minimizes \texttt{RMSE} is sought.
\texttt{dvs} is a divisor for splitting the interval to transform it
into a sequence of values among which the value that minimizes
\texttt{RMSE} is sought. For this purpose, the sequence step is
calculated as follows: \[
step = \frac{end - start}{dvs}
\]

@@

In fact, the \texttt{seq} function is called internally to generate the
sequence during the execution of the \texttt{model.tune.param\_range}
function.

tune\_dir\_path

To improve performance, the algorithm caches intermediate results in the
file system. This parameter specifies the path to the directory where
the cache files are saved.

cache\_file\_base\_name

The algorithm generates unique names for cache files based on this and
the \texttt{loop\_starter} parameter, as well as some other intermediate
values calculated during the execution.

fn\_tune.test.param\_value

This is a helper function name that is passed to the same-named
parameter of the {[}tune.model\_param{]} function that is called
internally during the execution (see the
\hyperref[func.tune.model_param]{description of the
\texttt{tune.model\_param} function} above).

\begin{itemize}
\tightlist
\item
  \textbf{max.identical.min\_RMSE.count:} ;
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{is.cv:} ;
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{endpoint.min\_diff:} ;
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{break.if\_min = TRUE:} A Boolean parameter that determines
  whether the function should terminate after completing the number of
  steps
\end{itemize}

specified by the parameter \texttt{steps.beyond\_min}, after the minimum
value of the \texttt{RMSE} has been found;

\begin{itemize}
\tightlist
\item
  \textbf{steps.beyond\_min = 2:} (takes effect only if
  \texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the
  number of steps after finding the minimum value of the \texttt{RMSE},
  upon completion of which the function should terminate.
\end{itemize}
